Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

The thesis main contributions are listed below :

@@

	\item First known garbage collectors that satisfy all the above-mentioned properties in both shared memory and distributed memory system is introduced in this thesis.
	\item Novel reference counting based technique is used to collect any garbage including cyclic garbage.    
	\item First known concurrent multi-collector reference counting based garbage collector is introduced in this thesis.

>>>>

The contributions of this thesis are listed below :

@@

	\item First known garbage collectors that satisfy all the above-mentioned properties in both shared memory and distributed memory systems.
	\item Novel hybrid reference counting and tracing techniques are used to collect any garbage including cyclic garbage.    
	\item First known concurrent multi-collector reference counting based garbage collectors.
